Empty Homes V1

### 2017-05-25 EmptyHomesV1.Rmd
Fixed error in functions
The cleaning function wasn't working properly

```{r setup}
setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
source("Setup.R")
```

#Load completed data

test <- read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")

unique(test$Exemption.type)

```{r}
# setwd(ShapeFiles)
# 
# wards.shp <- readShapeSpatial("London_Ward.shp")
# coords <- coordinates(wards.shp)
# WardsAdj <- poly2nb(wards.shp, queen= FALSE)
# plot(wards.shp, border="grey")
# plot(WardsAdj, coords, add=TRUE, col="red")
# 
# test <- (nb2mat(WardsAdj)>0)*1
# 
# 
# g=graph.data.frame(WardsAdj)
# get.adjacency(WardsAdj,sparse=FALSE)

@@

>>>>

```{r setup}
setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
source("Setup.R")

setwd(Functions)
list.files() %>% map(source)
```

@@

Lam2 <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%  
    StructureData(., lowuse = c(2:5,24,25), empty =  c(4:5,24,25))
